SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-21 quiz.tex
More quiz.

SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz...
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} in the form of Linked Open Data.

%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

Clover Quiz~\citep{cloverquiz} shows that ontologies can be used to automatically generate multiple-choice questions over DBpedia~\citep{dbpedia}.
To provide difficult wrong answers, the so called \emph{distractors}, we use direct neighbours of the classes that represent the correct answers.
Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.
%
%SNIK Quiz is freely available as an open source web application.
Because SNIK only contains the knowledge that the source textbooks describe, it does not contain the complete domain of Hospital Information Management.
As such, negative questions are problematic, as the given relationship could hold in the real world but not be described in the textbook source of the class.
The same problem concerns the distractors of positive questions.
So this problem cannot be avoided.
However, this is one of the reasons that we do not ask count questions like \enquote{How many functions is the CIO responsible for?}, which do not help much for learning anyways. % improve writing
Relationships could also hold implicitly through the subclass hierarchy.
For example, \aurl{bb}{ChiefInformationOfficer} is a subclass of \aurl{bb}{InformationManagementStaff}, which is responsible for \aurl{bb}{OperationalInformationManagement}.
It is unclear, whether the CIO is also responsible for operational information management.
%An ongoing bachelor's thesis~\citep{snikquiz} is investigating different strategies of generating complex questions, answers and distrators.

\subsection{Question Types}
%\paragraph{}

@@

\paragraph{closeMatch}
\begin{table}
\begin{tabular}{p{0.8\textwidth}  p{0.1\textwidth}}
\toprule
question	& correct\\
\midrule
In the Tactical Information Management, the Project Execution uses the Resource, while in the Strategic Information Management, the Project Execution uses the Resource.											&True \\
In the Strategic Information Management, the Project Management Board is responsible for  the Project Monitoring, while in the Tactical Information Management, the Project Steering Committee uses the Project.	&False \\
\bottomrule
\end{tabular}
\caption{Examples of generated \emph{closeMatch}-questions}
\label{tab:closematch}
\end{table}

This question type tests the connection between the textbooks \cite{ob} (tactical information management) and \cite{bb} (strategic information management) based on the existing \aurl{skos}{closeMatch} interlinks.
The aim is to help students transfer knowledge in one textbook to the other.
The questions have the form: In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object] with 2 possible answers: true and false.
Examplarly questions are given in \cref{tab:closematch}.

@@

\paragraph{Occurence}
Hier handelt es sich um eine Spezialisierung von close-by, bei der ent-
schieden werden soll, ob ein Begriff in keinem Buch, in Ammenwerth
u. a., 2014, in Winter u. a., 2011 oder in beiden Büchern auftritt. Eine
mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}. Auf diese Frage kann dann noch die Definition des Begriffes folgen, um noch mehr Kontext zu liefern.

\begin{table}
\begin{tabular}{p{0.5\textwidth}  p{0.3\textwidth}}
\toprule
Frage  & korrekt \\
\midrule
In which contexts does the term \enquote{Automated Observation} occur? & Tactical Information Management \\
In which contexts does the term \enquote{Health Insurance Company} occur? & Strategic Information Management \\
In which contexts does the term \enquote{System Analysis} occur? & Both Contexts \\
In which contexts does the term \enquote{System Administrator} occur? & Neither\\
\bottomrule
\end{tabular}
\caption[occurence-Ergebnisbeispiele]{Beispiele für generierte Fragen der \textit{occurence}-Strategie}
\label{tabelle:bsp_occurence}
\end{table}

\section{Results}\label{sec:application}
We apply this approach to SNIK and generate 1231 English questions using the templates described in \cref{tab:templates}.
It was used by students from the Universities of Amsterdam, Heidelberg and Leipzig during the international Frank van Swieten lectures in 2019.

@@

@@

We showed that knowledge on the management of information systems in medicine and health care is made publicly available using open standards over several interfaces with different compromises between expressivity and accessibility.
It can be combined with other knowledge in biomedical and health informatics and in other disciplines.

>>>>

SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz...
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract More abstract 
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

@@

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} in the form of Linked Open Data.
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction More introduction 
%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

Clover Quiz~\citep{cloverquiz} shows that ontologies can be used to automatically generate multiple-choice questions over DBpedia~\citep{dbpedia}.
To provide difficult wrong answers, the so called \emph{distractors}, we use direct neighbours of the classes that represent the correct answers.
Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.
%
%SNIK Quiz is freely available as an open source web application.
Because SNIK only contains the knowledge that the source textbooks describe, it does not contain the complete domain of Hospital Information Management.
As such, negative questions are problematic, as the given relationship could hold in the real world but not be described in the textbook source of the class.
The same problem concerns the distractors of positive questions.
So this problem cannot be avoided.
However, this is one of the reasons that we do not ask count questions like \enquote{How many functions is the CIO responsible for?}, which do not help much for learning anyways. % improve writing
Relationships could also hold implicitly through the subclass hierarchy.
For example, \aurl{bb}{ChiefInformationOfficer} is a subclass of \aurl{bb}{InformationManagementStaff}, which is responsible for \aurl{bb}{OperationalInformationManagement}.
It is unclear, whether the CIO is also responsible for operational information management.

% TODO: reformulate now that its not future work anymore but part of the paper
An ongoing bachelor's thesis~\citep{snikquiz} is investigating different strategies of generating complex questions, answers and distrators.

\subsection{Question Types}

TODO: Add the old question types, but only the b-versions (so no suffix is required in this paper)

\paragraph{definition}
describe definition-b...

\paragraph{label-definition}
describe label-definition...

\paragraph{contains}
describe contains...

@@

\paragraph{closeMatch}
\begin{table}[h]
\begin{tabulary}{\textwidth}{Ll}
\toprule
question	& correct\\
\midrule
In the Tactical Information Management, the Project Execution uses the Resource, while in the Strategic Information Management, the Project Execution uses the Resource.											&True \\
In the Strategic Information Management, the Project Management Board is responsible for  the Project Monitoring, while in the Tactical Information Management, the Project Steering Committee uses the Project.	&False \\
\bottomrule
\end{tabulary}
\caption{Examples of generated \emph{closeMatch}-questions}
\label{tab:closematch}
\end{table}

This question type tests the connection between the textbooks \cite{ob} (tactical information management) and \cite{bb} (strategic information management) based on the existing \aurl{skos}{closeMatch} interlinks.
The aim is to help students transfer knowledge in one textbook to the other.
The questions have the form: \emph{\enquote{In [Tactical / Strategic IM], the [subject] [predicate] the [object], while in [Strategic / Tactical IM], the [subject] [predicate] the [object].}} with two possible answers: true and false.
Examplarly questions are given in \cref{tab:closematch}.

@@

\paragraph{occurence}
\begin{table}[h]
\begin{tabulary}{\textwidth}{LL}
\toprule
question	&correct\\
\midrule
In which contexts does the term \enquote{Automated Observation} occur?		&Tactical Information Management \\
In which contexts does the term \enquote{Health Insurance Company} occur?	&Strategic Information Management \\
In which contexts does the term \enquote{System Analysis} occur?			&Both Contexts \\
In which contexts does the term \enquote{System Administrator} occur?		&Neither\\
\bottomrule
\end{tabulary}
\caption{Exemplary \emph{occurrence}-questions and correct answers.}
\label{tab:occurence}
\end{table}

The \emph{occurence} question type is a specialization of \emph{closeMatch}, where the student has to choose whether a term occurs in~\cite{ob},~\cite{bb}, in both textbooks or neither of them.
Exemplary questions are given in \cref{tab:occurence}.
%mögliche Frage ist hier: \enquote{In which books does the term \emph{Chief Information Officer} occur?}.
The context of the questions can be augmented with the definitions of the concepts.

\section{Results}\label{sec:application}
The question types definition-a and contains-a were used to generate 1231 English questions, see \cref{tab:templates}.
It was used by students from the Universities of Amsterdam, Heidelberg and Leipzig during the international Frank van Swieten lectures in 2019.

@@

\subsection{Evaluation}
\begin{table}[h]
\begin{tabularx}{\textwidth}{Xccc}
\toprule
Type				&rating interview 1	&rating interview 2	&rating interview 3\\
\midrule
label-definition	&3				&4				&3\\
definition-b		&4				&6				&3\\
contains-b			&5--6			&7				&6\\
\midrule
intertwined			&7				&7--8			&8\\
closeMatch			&8				&7--8			&8\\
occurence			&7				&5				&7\\
\bottomrule
\end{tabularx}
\caption{Rating given by interviewees based on the complexity of the questions on a scale between 1 and 10 with 10 representing maximum complexity.}
\label{tabelle:eval_komplex}
\end{table}

@@

%We showed that knowledge on the management of information systems in medicine and health care is made publicly available using open standards over several interfaces with different compromises between expressivity and accessibility.
%It can be combined with other knowledge in biomedical and health informatics and in other disciplines.
